---
title: "MA678_Report"
author: "Yirong Yuan"
date: "2022-12-11"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

Github Link:<https://github.com/yiryuan/MA678_Final_Project.git>

### **\<Abstract\>**

This project focuses on estimating the price of Boston Airbnb. In this
project, I used the dataset which is downloaded from
<http://data.insideairbnb.com/united-states/ma/boston/2022-09-15/visualisations/listings.csv.>
To estimate the price, I explored how factors, such as room type,
minimum night, and so on, influenced the price of Boston Airbnb. The
project has two parts: Exploratory Data Analysis and Multilevel Bayesian
Analysis. Exploratory Data Analysis visually displayed the relationship
between factor and price. In Multilevel Bayesian Analysis, I fitted a
multilevel model based on the different neighborhoods to Airbnb prices
for rentals in the Boston market to investigate the neighborhood
heterogeneity.

```{r,include=FALSE}
library(dplyr)
library(magrittr)
library(readr)
library(tidyverse)
library(tidytext)
library(wordcloud)
library(MASS)
library(ggplot2)
library(hrbrthemes)
library(leaflet)
library(viridis)
library(arm)
library(lme4)
library(metaSEM)
library(lmerTest)
library(bayesplot)
library(rstanarm)
Boston_Airbnb <- read_csv("/Users/yirong/Desktop/listings.csv")
```

### **\<Introducation\>**

#### **\<Background\>**

Since 2007, Airbnb (ABNB) has been an online marketplace that connects
people who want to rent out their homes with people looking for
accommodations in specific locales. Today, Airbnb is a service operated
and recognized around the world. Data analysis of the millions of
listings offered through Airbnb is a critical element of the company.
The massive amounts of data can be analyzed and used for security,
business decision-making, understanding customer and provider (host)
behavior and performance on the platform, guiding marketing programs,
implementing innovative add-ons Serve, and more.

Location is key to valuable real estate. Homes in cities with little
room for expansion are more beneficial than those with plenty of space.
Consider the accessibility, appearance, and amenities of a neighborhood,
as well as development plans. The community also influences the price of
Airbnb.

#### **\<Data\>**

I selected the target variable 'price' and a subset of 9 predictor
variables from the original data listings.csv. I deleted the rows in
which the prices of Airbnb are negative because it did not make sense.

**id**: The Airbnb id number

**price**: the Airbnb price

**latitude and longitude**: The geographical information

**neighbourhood**: The name of neighbourhood

**room_type**: Type of room (Entire home/apt, Private room and Shared
room)

**minimum_nights**: The minimum number of nights that a guest can book 

**number\_ of_reviews**: Total number of Airbnb guest ratings

**availability_365:** The total number of days the listing is available
for during the year 

```{r,include=FALSE}
## Delete the columns which only have a value
cnames <- colnames(Boston_Airbnb)
x <- 1:dim(Boston_Airbnb)[2]
T <- NULL
for(i in x){T <- c(T, dim(unique(Boston_Airbnb[i]))[1])}
drop_cols <- cnames[which(T == 1)]
Boston_Airbnb %<>% dplyr::select(!all_of(drop_cols))
##Select the columns that will be used in later analysis
Boston_Airbnb_Selected<-Boston_Airbnb %>% dplyr::select(id,name,neighbourhood,
                                                        latitude,longitude,room_type,
                                                        price, minimum_nights,number_of_reviews,
                                                        availability_365)
##ensure there is no NA in the data frame
na_value<-which(is.na(Boston_Airbnb_Selected))

##Delete the rows which prices of airbnb is negative 
Boston_Airbnb_Selected<-Boston_Airbnb_Selected %>% filter(price > 0)

##summary the data frame and make a suset to do data visualization better
summary(Boston_Airbnb_Selected)
subset_price <-Boston_Airbnb_Selected %>% filter(price <500)
```

### \<Method\>

#### \<Exploratory Data Analysis\>

Figures 2 and 3 both display the relationship between price and
geography. Figure 2 shows the detailed geographic location of the
listings. Figure 3 shows more clearly the price situation in different
neighborhoods. Figure 4 shows the relationship between listings' prices
and minimum nights in different neighborhoods and housing types. Figure
5 shows the relationship between listings' prices and the number of
reviews in different neighborhoods and housing types.

```{r,warning=FALSE,message=FALSE,echo=FALSE}
##See what words always are used to describe  Boston Airbnb name room
description <- data.frame(Boston_Airbnb$name)
description<-description %>% unnest_tokens(word, Boston_Airbnb.name)
data(stop_words)
description <- description %>% anti_join(stop_words)
description <- description %>% count(word, sort = TRUE) 
description%>% with(wordcloud(word, n, max.words = 50, random.order = FALSE, rot.per = 0.35, 
                          colors = brewer.pal(8, "Dark2")))
##display the price distribution in Boston
pal <-colorNumeric(palette = rainbow(6),domain = Boston_Airbnb_Selected$price)
p2<-leaflet(data = Boston_Airbnb_Selected) %>%  
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~longitude, ~latitude, color = ~pal(price), weight = 1, radius=1.5,
                   fillOpacity = 1, opacity = 1,label = paste("Neighbourhood:",Boston_Airbnb_Selected$neighbourhood)) %>% 
  addLegend("bottomright", pal = pal, values = ~price,title = "price(dollar)",opacity = 1)
p2


#display the data as they exist spatially spread out geographically.
p3<-ggplot(Boston_Airbnb_Selected,aes(x=longitude,y=latitude,size=price,color=neighbourhood)) + 
    geom_point(alpha=0.3) + 
    guides(color='none') +
    coord_fixed(1.3) + 
    scale_size(labels = scales::dollar,breaks = signif(10^seq(5,9,0.5),2)) +
    ggtitle( 
      "Boston, MA, Spatial Layout of Housing Data",
      "colored by neighbourhood and sized by price" 
    )
p3


p4<-ggplot(subset_price,aes(x=minimum_nights,y=price,color=room_type,shape=room_type))+
   geom_point(alpha=0.7,size=3) + 
  scale_y_log10(labels=scales::dollar) + 
  facet_wrap(~ neighbourhood, nrow=5, ncol=6) +
  theme_classic() +
  ggtitle(
    "Price vs. Minimum_night", 
    "by neighbourhood and colored by room_type indicator" )

p4

p5<-ggplot(subset_price,aes(x=number_of_reviews,y=price,color=room_type,shape=room_type))+
   geom_point(alpha=0.7,size=3) + 
  scale_y_log10(labels=scales::dollar) + 
  facet_wrap(~ neighbourhood, nrow=5, ncol=6) +
  theme_classic() +
  ggtitle(
    "Price vs. Number_of_review", 
    "by neighbourhood and colored by room_type indicator" )
p5


```

#### \<Multilevel Bayesian Analysis\>

```{r,warning=FALSE,message=FALSE,cache=FALSE,eval=FALSE}
M1<-stan_glmer(price~latitude+longitude+factor(room_type)+minimum_nights+number_of_reviews+availability_365+(1|neighbourhood),data=Boston_Airbnb_Selected)

M2<-stan_glmer(price~latitude+longitude+factor(room_type)+minimum_nights+number_of_reviews+availability_365+(1|neighbourhood),family = neg_binomial_2,data=Boston_Airbnb_Selected)
```

```{r,warning=FALSE,message=FALSE,include=FALSE}
M1<-stan_glmer(price~latitude+longitude+factor(room_type)+minimum_nights+number_of_reviews+availability_365+(1|neighbourhood),data=Boston_Airbnb_Selected)


M2<-stan_glmer(price~latitude+longitude+factor(room_type)+minimum_nights+number_of_reviews+availability_365+(1|neighbourhood),family = neg_binomial_2,data=Boston_Airbnb_Selected)

```


```{r,r,warning=FALSE,message=FALSE,echo=FALSE}
pp_check(M1)+ xlim(0, 500)
pp_check(M2)+ xlim(0, 500)
partial_data<-{M2} %T>% print()
partial_data<-partial_data %>% 
  coef() %$% neighbourhood %>%
  rownames_to_column("neighbourhood") %>% 
  as_tibble() %>%
  dplyr::select(neighbourhood,contains("Intercept")) %>%
  setNames(c("neighbourhood","base_price")) %>%
  mutate(base_price = exp(base_price)) %>%
  right_join( Boston_Airbnb_Selected)%>% mutate(neighbourhood=as.character(neighbourhood)) %>%
  mutate(neighbourhood = factor(neighbourhood,levels=unique(neighbourhood[order(base_price)]))) 

ggplot(partial_data,aes(x=longitude,y=latitude,size=price,color=neighbourhood)) + 
    geom_point(alpha=0.3) + 
    guides(color='none') +
    coord_fixed(1.3) + 
    scale_size(labels = scales::dollar,breaks = signif(10^seq(5,9,0.5),2)) +
    ggtitle( 
      "Boston, MA, Spatial Layout of Housing Data",
      "colored by neighbourhood and sized by price" 
    )

```

### **\<Result\>**

I first tried to fit the multilevel models and then used the posterior
predictive checking model to check these two models. The plots show the
model with a negative binomial argument worked better(plot 2).

I arrived at the following formula of fixed effect:

Price = -93.7+ 2.9 \* latitude + 0.3\* longitude + 0.6\* Hotel room -0.8
\*Private room -1.1\* shared room

The model shows that latitude, longitude, and price are positively
correlated. Hotel rooms will make room prices more expensive, while
private and shared rooms will make room prices cheaper. Some
neighborhoods positively correlate with the price(such as Back bay,
Chinatown, downtown, Fenway, Harbor Islands, North End, South Boston
Waterfront, and West Roxbury.

In the last plot, I color the neighborhood according to the ordering
dictated by the estimated price intercepts (base_price). This way, the
higher-priced areas will be more toward the red end of the color
spectrum.

### **\<Discussion\>**

I found the relationship between price and geography, and room type
through the multilevel model. But I didn't find an association between
price, minimum nights, and the number of reviews by the multilevel
model. The previous EDA shows that the minimum nights and number of
reviews are related to the price. Further research is needed on them.

As seen from the posterior predictive checking model, my multilevel
model does not fit perfectly, probably because of variables and data
limitations. The fit of the price prediction model can be improved in
the future.

### **\<Appendix\>**

```{r,warning=FALSE,message=FALSE,echo=FALSE}

##make a plot to see the density and distribution of prices for each neigherhood
A1 <- subset_price%>%
  ggplot( aes(x=price, color=neighbourhood, fill=neighbourhood)) +
    geom_histogram(alpha=0.6, binwidth = 5) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("") +
    ylab("Assigned Probability (%)") +
    facet_wrap(~neighbourhood) 
A1

##Density and distribution of prices for other predictors
A2<-subset_price %>% filter(minimum_nights<200) %>% ggplot(aes(x=minimum_nights)) +
    geom_histogram( binwidth=3, fill="#69b3a2", color="#e9ecef", alpha=0.9) +
    theme_ipsum() +
    theme( plot.title = element_text(size=15))
A2

A3<-subset_price %>% filter(number_of_reviews<300)%>% ggplot(aes(x=number_of_reviews)) +
    geom_histogram( binwidth=3, fill="#404080", color="#e9ecef", alpha=0.9) +
    theme_ipsum() +
    theme(plot.title = element_text(size=15))
A3

A4<-subset_price %>%  ggplot(aes(x=availability_365)) +
    geom_histogram( binwidth=3, fill="#999999", color="#e9ecef", alpha=0.9) +
    theme_ipsum() +
    theme(plot.title = element_text(size=15))
A4

##Density and distribution of prices for each room Type
A5<-subset_price%>% 
  ggplot(aes(x=room_type, y=price, fill=room_type)) +
  geom_boxplot(show.legend = FALSE) + coord_flip() 
A5

summary(M2)

```
